### Application #2 - Evaluating Rural-Urban-Suburban Designations
```{r}
data("midwest")
## Restrict the variables used in the clustering
midwest2 <- select(midwest, county, state, popdensity, 
                   percwhite, percblack, percasian, perchsd, 
                   percollege, percprof, percchildbelowpovert, 
                   percadultpoverty, percelderlypoverty)
```
Question 1: Evaluating optimal number of clusters for unscaled data: 

```{r}
#elbow
```

```{r}
#silhouette
```

```{r}
#gap statistic
```
Using 3 clusters does/doesn't seem reasonable because...

Question 2: Finding Urban Centers Cluster

Apply k-means clustering with k=3 to the unscaled data:
```{r}
```
Does one of the three clusters appear to describe the urban centers of Chicago (Cook County IL), Cleveland (Cuyahoga County OH), Detroit (Wayne County MI), Milwaukee (Milwaukee County WI), and Indianapolis (Marion County IN)?

Question 3: Again using k-means clustering with k=3 on the unscaled data, does the smaller of the two remaining clusters appear to describe suburban counties? If you aren’t familiar with the geography of the Midwest, try googling a few of the counties you see in this cluster to gauge their proximity to large cities mentioned in the prior question.

```{r}
```

Question 4: Using the scaled data, assess whether using 3 clusters seems reasonable. Briefly describe your thoughts.

```{r}
#rescale data because popdensity is much larger than the other variables, which are percentages
```
Question 5: Using k-means clustering with k = 3 on the scaled data, do these clusters appear to correspond with “rural”, “urban”, and “suburban”? (Hint: start by locating the same large cities mentioned earlier)

```{r}
```
Question 6:  Based upon what you’ve seen so far in this application, do you prefer the original or scaled approach? Briefly provide an argument in support of each approach.
