---
title: "Clustering Application #1 - Customer Segmentation"
author: "LaAnna Farnelli, Aru Fatehpuria & Emma Foulkes"
date: "April 22, 2019"
output: html_document

```{r}
data <- read.csv("https://remiller1450.github.io/data/OnlineRetail.csv") ## This takes a long time, the data contain >500k records
data <- data[complete.cases(data),] # restrict the data to records with complete information
#derive Recency, Frequency, and Monetary value:
dates <- as.Date(substr(data$InvoiceDate,1,10), "%m/%d/%Y") ## Extract only the date, specifying its format
data$days_since <-  as.Date("2011-12-10") - dates ## Subtract from a reference date
## Keep only the minimum per customer
Rec <- data %>% group_by(CustomerID) %>% summarise(min = min(days_since))
Rec <- as.numeric(Rec)
```
```{r}
library(factoextra)
library(dplyr)
library(tidyr)
library(ggplot2)
library(cluster)
```
## Questions 1-2: Creating new variables

First, we create Freq containing the number of purchases by each customer:
```{r}
Freq <- data %>%
group_by(CustomerID) %>%
summarize(count = n()) #based on Hint: The command summarize(count = n()) will return the number of rows...
```

Next we can create a vector Mon containing the total purchased amount by each customer:

```{r}
Mon <- data %>%
group_by(CustomerID) %>%
summarize(total_purchase = sum(Quantity*UnitPrice))
```

## Question 3: Creating new data.frame CD 

CD should have one row per customer, containing the three variables (Rec, Freq, and Mon) corresponding to that customer:

```{r}
CD <- left_join(x = Rec, y = Mon, by = "CustomerID")
CD <- left_join(x = CD, y = Freq, by = "CustomerID")
names(CD)[names(CD)=="min"] <- "Rec"
names(CD)[names(CD)=="total_purchase"] <- "Mon"
names(CD)[names(CD)=="count"] <- "Freq"
CD = subset(CD, select = -(CustomerID))
```

## Question 4: Constructing the Boxplots

```{r}
CD1 <- gather(CD, key = "Var", value = "Val") #based on Hint: consider using gather to create a “long” version of your CD data.frame
CD1 <- separate(CD1, col = "Var", into = c("Model"))
ggplot(CD1, aes(x = , y = Val)) + geom_boxplot() + coord_flip() + facet_wrap(~ Model, scales = "free") + labs(title="RFM Variable Distributions") #add title “RFM Variable Distributions” according to instructions
```
Filtering and Transforming (from assignment sheet):

```{r}
CD$Rec <- as.numeric(as.character(Rec$min))
CD <- filter(CD, Mon > 0) # remove customers with negative monetary values (they returned items)
CD$Mon <- log10(CD$Mon) # apply a log transformation based on the extreme right skew (large number of outliers)
CD$Freq <- log10(CD$Freq)
```

## Question 5: k-means clustering on the newly transformed data

```{r}
#standardize the data (notice the difference scales of Rec and Mon for example): 
CD <- scale(CD, center = TRUE, scale = TRUE)
#select an optimal number of clusters using one of the methods we’ve covered: 
fviz_nbclust(CD, kmeans, method = "silhouette", k.max = 8)
#visualize clusters using three different scatter plots (showing the three unique pairings of variables):
k1 <- kmeans(CD, centers = 2, nstart = 25)  
CD <- as.data.frame(CD)
ggplot(CD, aes(x=Rec, y=Mon)) + geom_point()
```
People who have  gone to the store recently are more likely to spend more money than people, or at least a wider range of amounts, as compared to people who have not gone to the store recently.

```{r}
ggplot(CD, aes(x=Mon, y=Freq)) + geom_point()
```
People who spend more money at the store are more likely to buy the products in larger quantities. 

```{r}
ggplot(CD, aes(x=Rec, y=Freq)) + geom_point()
```
People who have been to the store recently are more likely to buy a wider range of amount of products whereas people who have not been to the store recently are likely to buy lower amount of products.

