### Application #2 - Evaluating Rural-Urban-Suburban Designations
```{r}
data("midwest")
## Restrict the variables used in the clustering
midwest2 <- select(midwest, county, state, popdensity, 
                   percwhite, percblack, percasian, perchsd, 
                   percollege, percprof, percchildbelowpovert, 
                   percadultpoverty, percelderlypoverty)
```
Question 1: Evaluating optimal number of clusters for unscaled data: 

```{r}
#elbow
```

```{r}
#silhouette
```

```{r}
#gap statistic
```
Using 3 clusters does/doesn't seem reasonable because...

Question 2: Finding Urban Centers Cluster

Apply k-means clustering with k=3 to the unscaled data:
```{r}
```
Cluster [NAME] describes the urban centers of Chicago (Cook County IL), Cleveland (Cuyahoga County OH), Detroit (Wayne County MI), Milwaukee (Milwaukee County WI), and Indianapolis (Marion County IN)...

Question 3: Determining Suburban Cluster

The two remaining clusters are [NAME] and [NAME]. The smaller one does/doesn't appear to describe suburban counties because...
//mention proximity...

Question 4: Thoughts on using 3 clusters

Our assessment...

```{r}
#rescale data because popdensity is much larger than the other variables, which are percentages
```
Question 5: Finding Urban/Rural Clusters in Scaled Data

```{r}
#Apply k-means clustering with k=3 to the unscaled data
```
Rural cluster:
Urban cluster:
Suburban cluster: 

```{r}
```
Question 6: Unscaled/Scaled Preference
Our thoughts... 
Unscaled is good for...
Scaled is good because...
