title: "Clustering Application #3 - Geography of Plant Species"
author: "LaAnna Farnelli, Aru Fatehpuria & Emma Foulkes"
date: "April 22, 2019"
output: html_document

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(factoextra)
library(cluster)
library(dplyr)
```

## Data Set-Up

The following code is setup from your example and application description in the Clustering Lab document:
```{r}
## Location of the raw data
file <- "https://remiller1450.github.io/data/plants.data"

## Get the number of variables (number of unique fields)
no_col <- max(count.fields(file, sep = ","))
plants <- read.table(file,sep=",",fill=TRUE,header = F,col.names=c(1:no_col))

## To make this more manageable we'll use 1000 randomly selected rows
set.seed(123)
random_sample <- sample(1:nrow(plants), size = 1000)
plants <- plants[random_sample,]
names <- plants$X1 ## Extract the plant names
locations <- levels(unlist(plants[,2:no_col])) ## Extract unique locations
locations <- locations[-which(locations == "")] ## Remove empty the location

## Set up an empty X matrix to be filled
X <- matrix(0, nrow = nrow(plants), ncol = length(locations)) 
colnames(X) <- as.character(locations) ## Name its variables

## Fill the X matrix with 1s where appropriate (location is present for that species)
## Warning: looping tends to be slow in R
for(i in 1:nrow(X)) {
    X[i,] <- as.numeric(colnames(X) %in% as.character(unlist(plants[i,-1])))
}
## Code each column as a binary factor variable
XF <- as.data.frame(apply(X, 2, as.factor))
D <- daisy(XF, metric = "gower") #use the daisy function to calculate Gower distance
```

##Question 1

```{r}
D <- daisy(XF, metric = "gower") #using daisy function to calculate Gower distance
pm <- pam(D, k = 2) ## Apply pam clustering with k = 2
pm$silinfo$avg.width  ## checking Average silhouette width to keep it closer to 1 than -1
```

I chose 2 clusters because that k value yields a higher average silhouette width (.72, closest to 1) of all the options between k=2 and k=10. I will be interpreting cluster #2 in the following question.

## Question 2

```{r}
hc <- hclust(D)
dend1 <- as.dendrogram(hc)
dend2 <- cut(dend1, h = 0.65) ## Cut the dendrogram
plot(dend2$upper)  ## Plot the cut tree
hc_cut <- cutree(hc, h = 0.65) ## Apply the same cut to the hc cluster object
table(hc_cut) ## Cluster frequencies
```

My interpretation of the 2nd cluster:

```{r}
colMeans(X[hc_cut == 2,]) ## Interpret 2nd cluster

clusplot(pm, main = "Cluster Plot, k=2", color = TRUE)
```

## Question 3

There is no definitive answer since cluster analysis is essentially an exploratory approach; the interpretation of the resulting hierarchical structure is context-dependent and often several solutions are equally good from a theoretical point of view. You can use stop-criteria for agglomerative hierarchical clustering including visual criteria, e.g. silhouette plots, and some kind of numerical criteria. Basically, we want to know how well the original distance matrix is approximated in the cluster space. I also use k-means, with several starting values, and the gap statistic (mirror) to determine the number of clusters that minimize the within-SS. 
